---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)


decathlon_clean <- read_csv(here::here("clean_data/decathlon_clean.csv"))
```

# Q1. Who had the longest long jump seen in the data?
```{r}
decathlon_clean %>% 
  select(athlete_name, competition, event, score) %>% 
  filter(event == "long_jump") %>% 
  slice_max(score)

# Comment: 
# Was Clay in OlympicG with a jump of 7.96 meters.
```

# Q2. What was the average 100m time in each competition?
```{r}
decathlon_clean %>%
  select(competition, event, score) %>% 
  filter(event == "100_m") %>% 
  group_by(competition) %>% 
  summarise(avg_100_m_per_competition = 
              as.numeric(format(mean(score), digits = 5))
  ) 

# Comment: 
# In Decastar competition the average of 100m event was 11.175 and in
# OlympicG competition was 10.916.
```
In Decastar competition the average of 100m event was 11.175 and in
OlympicG competition was 10.916.


# Q3. Who had the highest total points across both competitions?
```{r}
decathlon_clean %>%
  select(athlete_name, competition, points) %>% 
  group_by(competition) %>% 
  arrange(desc(points)) %>% 
  head(1) 

# Comments:
# Was the athlete Sebrle in OlympicG competition with a total of 8893  points.
```
Was the athlete Sebrle in OlympicG competition with a total of 8893  points.

# Q4. What was the shot-put scores for the top 3 competitors in each competition?
```{r}
decathlon_clean %>% 
  select(athlete_name, competition, event, score) %>% 
  filter(event == "shot_put") %>% 
  group_by(competition) %>% 
  slice_max(score, n = 3) %>% 
  arrange(desc(score))
```
 Comments:
    In OlympicG competition, in first was Karpov with 16.36, in second Karpov
 with 15.93 and in third Macey with 15.73.

    In Decastar competition, in first was Karpov with 16.36, in second Karpov
 with 15.93 and in third Macey with 15.73.

Q5. What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?

```{r}
# This function allow us to know what is the mean for who ran above and bellow 
# of a certain time (in seconds) in a 400m event.
#  --Arguments-- 
#    1) data_frame:   insert which data frame we are using
#    2) select_score: insert the time (seconds) that you want (e.g. 50, 49...)
#    
#  -- Details --
#     For select_score argument, the values just be numeric and between the 
#  range of values that exist in the current data frame.

my_function <- function(data_frame, select_score){
  library(assertr)
  
  # 1 - Ensure inserted score is between range values that are in table
  # 1.1 - Find out what is the higher score value
  max_400m_score <- data_frame %>%
    filter(event == "400_m") %>% 
    slice_max(score) %>% 
    pull()
  
  # 1.2 - Find out what is the lower score value
  min_400m_score <- data_frame %>%
    filter(event == "400_m") %>% 
    slice_min(score) %>% 
    pull()
  
  data_frame %>%
    verify(between(select_score, min_400m_score, max_400m_score))
  
  # 2 - add a condition, that makes sure just ONLY in numeric input
  if (!is.numeric(select_score)){
    stop("A non-numeric value was inserted. Just numeric values are allowed")
  }
  
  # 3 - Calculate the average points values
  # 3.1 - Average points values for who run bellow select_score seconds
  mean_points_below_400m <- data_frame %>% 
    filter(event == "400_m" & score < select_score) %>% 
    summarise(mean_score_below_50_sec = 
                as.numeric(format(mean(points)), digits = 7)) %>% 
    pull()
  
  # 3.2 - Average points values for who run above select_score seconds
  mean_points_above_400m <- data_frame %>% 
    filter(event == "400_m" & score > select_score) %>% 
    summarise(mean_score_below_50_sec = 
                as.numeric(format(mean(points)),digits = 7)) %>% 
    pull() 
    
  
  # 4 - Output
  # 4.1 - Writen output
  phrase <- paste("The average points for who ran the 400 meters bellow", select_score, "was", mean_points_below_400m, "and for who ran above", select_score, " was", mean_points_above_400m)
  
  print(phrase)
  
  #4.2 - Table output
  table <- bind_rows(
    c(label = str_c("bellow_", select_score), mean_points = mean_points_below_400m),
    c(label = str_c("above_", select_score),  mean_points = mean_points_above_400m)
  )
  return(table)
  
}

my_function(decathlon_clean, 50)
```