---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)

candy_data_clean <- read_csv(here::here("clean_data/candy_data_clean.csv"))
```

#Q1: What is the total number of candy ratings given across the three years?
```{r}
candy_drop_na_answer <- candy_data_clean %>% 
  drop_na(answer)


candy_drop_na_answer %>% 
  summarise(count_candy_rated = sum(n()))
```
Had rating 630368	candy's across the three years, since 2015 to 2017.



#Q2: What was the average age of people who are going out trick or treating?
```{r}
candy_drop_na_age <- candy_data_clean %>% 
   drop_na(age)

candy_drop_na_age %>% 
  filter(going_out == TRUE) %>% 
  summarise(avr_age_going_out = mean(age))
```
The average of people who are going out trick or treating was 34,9 years old.



#Q3 :What was the average age of people who are not going trick or treating?
```{r}
candy_drop_na_age %>% 
  filter(going_out == FALSE) %>% 
  summarise(avr_age_not_going_out = mean(age))
```
The average of people who are not going out trick or treating was 39 years old.



#Q4: For each of joy, despair and meh, which candy bar received the most of these ratings?
```{r}
higher_candy_joy <- candy_drop_na_answer %>% 
  filter(answer == "JOY") %>% 
  group_by(candy) %>% 
  summarise(count_higher_joy = sum(n())) %>% 
  arrange(desc(count_higher_joy)) %>% 
  head(1)

higher_candy_despair <- candy_drop_na_answer %>% 
  filter(answer == "DESPAIR") %>% 
  group_by(candy) %>% 
  summarise(count_higher_despair = sum(n())) %>% 
  arrange(desc(count_higher_despair)) %>% 
  head(1)

higher_candy_meh <- candy_drop_na_answer %>% 
  filter(answer == "MEH") %>% 
  group_by(candy) %>% 
  summarise(count_higher_meh = sum(n())) %>% 
  arrange(desc(count_higher_meh)) %>% 
  head(1) 

bind_rows(
  c(higher_candy_joy),
  c(higher_candy_despair),
  c(higher_candy_meh)
)

```
For joy was 'reese_s_peanut_butter_cups' with 7369, for despair was 
'broken_glow_stick' with 7905 and meh with 1570 was lollipops.


#Q5:How many people rated Starburst as despair?
```{r}
candy_data_clean %>% 
  filter(candy == "starburst", answer == "DESPAIR") %>% 
  summarise(count_starburst_despair = sum(n()))
```
There were 1990 people who rated starburst as despair.





```{r}
# This function count despair as -1, joy as +1, and meh as 0. As output, it 
# get higher total score/points by the variables grouped.
# This function have two arguments:
#       - data_set:     the name of the data we are using
#       - grp_variable: the variables that we will group

score_function <- function(data_set, grp_variables){
  data_set %>% 
    mutate(score = recode(
      answer,
      "JOY"     = 1,
      "MEH"     = 0,
      "DESPAIR" = -1)
    ) %>% 
    group_by_at (grp_variables) %>% 
    summarise (count_score = sum(score, na.rm = TRUE)) %>% 
    slice_max (count_score)
}
```

#Q6: What was the most popular candy bar by this rating system for each gender in the dataset ?
```{r}
score_function(
  data_set      = candy_data_clean,
  grp_variables = vars(gender, candy)
) %>% 
  filter(!gender == "NA")
```
By gender, the most popular candy was reese_s_peanut_butter_cups for females 
(768 points) and for males (1443 points). For "I'd rather not say", kit kat got
62 points and for "other" was twix with 32 points.



#Q7: What was the most popular candy bar in each year?
```{r}
score_function(
  data_set      = candy_data_clean,
  grp_variables = vars(year, candy)
)
```
In 2015 and 2017 the most popular candy was "reese_s_peanut_butter_cups" with 
4375 points and 1403 points. In 2016 was kit_kat with 920 points.



#Q8: What was the most popular candy bar by this rating for people in US, Canada, UK, and all other countries?
```{r}
# was needed to classify the countries that are not USA, UK and Canada as 
# 'other country'. Our data was saved in a variable called 'candy_country' to be
# used the function 'score_function()'.
candy_country <- candy_data_clean %>% 
  mutate(country = if_else(
    country %in% c("USA", "UK", "Canada"),
    country,
    "other country"))

score_function(
  data_set      = candy_country,
  grp_variables = vars(country, candy)
)
```
The most popular candy rating by country rating was:
 - in Canada, was kit kat with 229 points;
 - in USA, rolos with 1968 points;
 - in UK, were lindt truffle and rolos both with 30 points; and
 - in the other countries presented in our data, "reese_s_peanut_butter_cups" got 1968 points.
